Technical Report

### 2018-06-16 fully-abstract-comp/technical-report.tex
Changed and proved one of the lemmas needed to prove the safe implies reasonable lemma.

\begin{lemma}
  \label{lem:codereg-Hsigma-not-lrv}
  If $\dom(\code) \subseteq \ta$, $n > 0$ and $\sigma \in (\sigrets \uplus \sigcloss)$, then $\codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}.H_\sigma~ \sigma \not\nequal \lrv$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{lemma}
  \label{lem:codereg-not-read-write}
  If $\pwheap(r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$ and $a \in \dom(\code)$ and $\memSat{\code \uplus \ms_S,\stk,\ms_\stk,\ms_T}{W}$ and $\sigrets \neq \emptyset$, then
  \begin{itemize}
  \item $\npair{\{a\}} \not\in \readCond{\normal,W}$
    % \item $\npair{\{a\}} \not\in \writeCond{\normal,W}$
    % It seems unnecessary to show the part about the write condition as all non-no-perm permissions have read.
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

>>>>

\begin{lemma}
  \label{lem:codereg-Hsigma-not-lrv}
  If $\dom(\code) \subseteq \ta$, $n > 0$ and $\sigma \in (\sigrets \uplus \sigcloss)$, then $\codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}.H_\sigma \sigma \not\nequal \lrv$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{lemma}
  \label{lem:codereg-not-read-write}
  If $n > 0$, $\dom(\code) \subseteq \ta$, $\gc = (\ta,\stkb)$, $\pwheap(r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$ and $a \in \dom(\code)$ and $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$ and $\sigrets \neq \emptyset$, then
  \begin{itemize}
  \item $\npair{\{a\}} \not\in \readCond{\normal,W}$
    % \item $\npair{\{a\}} \not\in \writeCond{\normal,W}$
    % It seems unnecessary to show the part about the write condition as all non-no-perm permissions have read.
  \end{itemize}
\end{lemma}
\begin{proof}
  For the sake of contradiction assume $\npair{\{a\}} \in \readCond{\normal,W}$.
  Then there exists $S \subseteq \addressable{\lin, \pwheap}$ and $R : S \fun
  \powerset{\nats}$ such that
  \begin{itemize}
  \item $\biguplus_{r\in S} R(r) \supseteq A$
  \item $\forall r \in S \ldotp \pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$
  \end{itemize}
  We claim that $r_\code \in S$\lau{TODO: show this claim}.
  If this is indeed the case, then we have $\pwheap(r_\code).H \nsubeq \stdreg{\dom(\code),\gc}{\pur}.H$ (we must have $R(r_\code) = \dom(\code)$ as the two regions couldn't be $\nequal$ otherwise).
  This means that for all $a \in \dom(\code)$ and $n' < n$ it must be the case that $\npair[n']{(\code(a),\code(a))} \in \lrv(W_a)$ for all $W_a$ that are compatible w.r.t.
  $\oplus$ and combine to be $W$.
  We know that $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$ and $\pwheap(r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$ from which we can deduce $\npair{(\code,\code)} \in H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; (\ta,\_) \; \xi^{-1}(W_\code)$ which in particular gives us $\sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code$.
  This in turns entails that for $\sigma \in \sigrets$ there exists some $a' \in \dom(\code)$ such that $\code(a') = \seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr}$ and $\sigma \in [\sigma_\baddr,\sigma_\eaddr]$.
  This means that for such a $\sigma$ and $a'$, it must be that case that
  $\npair[n']{(\seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr},\seal{\sigma_\aaddr,\sigma_\baddr,\sigma_\eaddr})}
  \in \lrv(W_{a'})$ which gives us
  $\codereg{\sigrets,\sigcloss,\code,\gc}.H_\sigma  \; \sigma \nequal \lrv$
  contradicting Lemma~\ref{lem:codereg-Hsigma-not-lrv}.

  It remains to show $r_\code \in S$.
  To show this, we assume for contradiction that $r_\code \not\in S$.
  This means that there exists $r \neq r_\code$ such that $a \in R(r)$ and $\pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$.
  Because we know $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, it must be possible to split up $\ms_S$ in disjoint memory segments that each (paired with a target memory segment) satisfies exactly one region.
  In this case, both $r$ and $r_\code$ needs a memory segment that has $a$ in the domain which means that no such disjoint union can exist which gives us a contradiction.
\end{proof}

\begin{lemma} 
  \label{lem:code-reg-and-mem-sat}
  If $\pwheap(r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$ and
  $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, then there exists $W''$
  and $W'$ such that $W = W' \oplus W''$ and
  $\npair{(\code,\code)} \in H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; \gc \; \xi^{-1}(W')$
\end{lemma}
\begin{proof}
  TODO
\end{proof}
